\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{refstyle}
\usepackage{csvsimple}
\author{\large Jay Lokhande}
\date{\today}
\begin{document}
\raggedright
\title{\huge \bf Bibliography}
\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{roman}

\newpage
\section{ Making Bibliography}

\subsection{Bibtex Method}

The intensification of senior population has been a concern worldwide ~\cite{Boney96}.Compared to the younger generations, the elderly always experience critical challenges in their activity of daily living (ADL) [2-4]. Rather disconcertingly, most of them are suffering degeneration and geriatric issues, which lead them to be dependent on a long-term medication intake. Consequently, this is causing them to be more vulnerable against potential harms in their living environment ~\cite{MG}.
Therefore, many elders prefer to reside in healthcare institutions rather than taking the risk of being less attended to and supported while being at home.\\ However, the absence of standardization management for elderly care institutions in the industry requires some working up. Currently, elderly centres have their particular regulations on administration which not only generates management gaps in operation but also slows down the development pace of the entire industry ~\cite{HK}.\\
Due to the many issues in geriatric care, routine medication plays an essential
role in the ADLs of many elderly. In this case, medicine mismanagement becomes
a lethal factor for the elderly in care centres. However, many centres are still
equipped with manually performed medicine closets Fig. 1, which post hidden
dangers of medicine retardation, mismatch or over dosage perhaps inadvertently or
by careless caregivers ~\cite{Pan}. 


\begin{thebibliography} {}

\bibitem{Boney96} Boney, L., Tewfik, A.H., and Hamdy, K.N., ``Digital
Watermarks for Audio Signals," \emph{Proceedings of the Third IEEE
International Conference on Multimedia}, pp. 473-480, June 1996.
\bibitem{MG} Goossens, M., Mittelbach, F., Samarin, \emph{A LaTeX
Companion}, Addison-Wesley, Reading, MA, 1994.
\bibitem{HK} Kopka, H., Daly P.W., \emph{A Guide to LaTeX},
Addison-Wesley, Reading, MA, 1999.
\bibitem{Pan} Pan, D., ``A Tutorial on MPEG/Audio Compression," \emph{IEEE
Multimedia}, Vol.2, pp.60-74, Summer 1998.
\end{thebibliography}
\end{document}